{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or: How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-10-26 thesis/thesis.tex
turns out oathbringer had a good quote after all
snakefight and parent acks

\noindent
grade distributions therein.
Mario Dehesa-Azuara generously contributed the
transactional memory data structures
that make up about half of Chapter~\ref{chap:tm}'s evaluation suite.

@@

@@

\chapter{Conclusion}
\label{chap:conclusion}
\inspirationalquote{
	\begin{tabular}{p{0.84\textwidth}}
	"If you are a god, Zeus, as the stories claim, then why did you create evolution?
	Why did you make a world that can only grow through cruelty and pain?"
	\\
	For a moment\inspirationalhyphen{}surely this meant death was near\inspirationalhyphen{}she thought she heard him answer:
	"My child, I was shaped by the gods that came before me, as you were shaped by me.
	The choice I had was between creation and oblivion, life and death.
	And I chose life, because any life is better than no life,
	because as long as there is life, there is hope\inspirationalhyphen{}if not for us, then for some generation to come."
	\\
	"Then how are you a god, if you can offer so little?" she whispered, feeling death creep closer.
	\\
	"I am a god because I take upon myself the burden of creation," the statue replied.
	\\
	"Then we are all gods," Alexandra said, and pushed the button.
	\end{tabular}}
%{Galatea, The Talos Principle}
{The Talos Principle}

>>>>

\noindent
grade distributions therein.
Mario Dehesa-Azuara generously contributed the
transactional memory data structures
that make up about half of Chapter~\ref{chap:tm}'s evaluation suite.
%
Carlo Angiuli, Evan Cavallo, Ziv Scully, Jim McCann,
Matthew Maurer, Stefan Muller, Guillaume Didier,
Sol Boucher, and Michael J. Sullivan
helped me rehearse and polish the snake fight talk.

@@

My parents, Eve and David Blum, and my grandparents, Margie Granach and Elsie Blum,
provided bottomless emotional support throughout my education.
I am grateful beyond words for the privileged life they provided
that allowed me the opportunity to pursue higher education.

@@

\chapter{Conclusion}
\label{chap:conclusion}
%\inspirationalquote{
%\begin{tabular}{p{0.6\textwidth}}
%"This is the end, right? The end of this story?"
%
%"We were always at the end. It's a free play, buddy. Clock's all zeroes."
%\end{tabular}}
%%{Nine \& Ten, 17776}
%{17776}
\inspirationalquote{
	\begin{tabular}{p{0.84\textwidth}}
	"If you are a god, Zeus, as the stories claim, then why did you create evolution?
	Why did you make a world that can only grow through cruelty and pain?"
	\\
	For a moment\inspirationalhyphen{}surely this meant death was near\inspirationalhyphen{}she thought she heard him answer:
	"My child, I was shaped by the gods that came before me, as you were shaped by me.
	The choice I had was between creation and oblivion, life and death.
	And I chose life, because any life is better than no life,
	because as long as there is life, there is hope\inspirationalhyphen{}if not for us, then for some generation to come."
	\\
	"Then how are you a god, if you can offer so little?" she whispered, feeling death creep closer.
	\\
	"I am a god because I take upon myself the burden of creation," the statue replied.
	\\
	"Then we are all gods," Alexandra said, and pushed the button.
	\end{tabular}}
%{Galatea, The Talos Principle}
{The Talos Principle}
